
% Just compile this file using pdflatex after making all required changes.

\documentclass[12pt,a4paper]{report}
\usepackage[pdftex]{graphicx} %for embedding images
\renewcommand{\baselinestretch}{1.5}
%\usepackage{url} %for proper url entries
\usepackage[bookmarks, colorlinks=false, pdfborder={0 0 0}, pdftitle={<pdf title here>}, pdfauthor={<author's name here>}, pdfsubject={<subject here>}, pdfkeywords={<keywords here>}]{hyperref} %for creating links in the pdf version and other additional pdf attributes, no effect on the printed document
%\usepackage[final]{pdfpages} %for embedding another pdf, remove if not required
\usepackage{geometry}
\usepackage[pdftex]{graphicx}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{fixltx2e}
\usepackage{multirow}
\usepackage{textcomp}

\geometry{
	left=2.2cm,
	top=2.54cm,
	bottom=2.921cm,
	right=1.5cm
}
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{}
\chead{}
\lfoot{\textit{Department of Computer Applications,CET}}
\cfoot{}
\rfoot{\thepage}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}
\begin{document}
\renewcommand\bibname{Bibliography} %Renames "Bibliography" to "References" on ref page

%include other pages
\input{./title.tex}
\input{./certificate.tex}
\input{./acknow.tex}
\input{./abstract.tex}


\pagenumbering{roman} %numbering before main content starts
\tableofcontents
\listoffigures

\newpage
\pagenumbering{arabic} %reset numbering to normal for the main content

    \input{introduction.tex}
    \input{chapter2styletransfer.tex}
    \input{chapter3gan.tex}
    \input{chapter4stylegan.tex}
    \input{conclusion.tex}

%%%%%%%%%%%%%%%%%%%%%%%% Bibilography

\begin{thebibliography}{9}
\bibitem{styletransfer} 
L. A. Gatys, A. S. Ecker, and M. Bethge.
\textit{ Image style transfer using convolutional neural networks.}
In Proc. CVPR, 2016.
 
\bibitem{GAN} 
I.Goodfellow, J.Pouget-Abadie, M.Mirza, B.Xu, D.Warde-Farley, S. Ozair, A.Courville, and Y.Bengio. 
\textit{ Generative Adversarial Networks.} In NIPS, 2014.
 
\bibitem{ADAM} 
D. P. Kingma and Jimmy Ba.
\textit{ Adam: A method for stochastic optimization.}  In ICLR, 2015.

\bibitem{backpropogation} 
D. J. Rezende, S. Mohamed, and D. Wierstra.
\textit{  Stochastic backpropagation and approximate inference in deep generative models.} In Proc. ICML, 2014

\bibitem{improved gan} 
T. Salimans, I. J. Goodfellow, W. Zaremba, V. Cheung, A. Radford, and X. Chen.
\textit{  Improved techniques for training GANs.}In NIPS, 2016.

\bibitem{avoid overfitting} 
N. Srivastava, G. Hinton, A. Krizhevsky, I. Sutskever, and R. Salakhutdinov.
\textit{  Dropout: A simple way to prevent neural networks from overfitting.}  Journal of Machine Learning Research, 15:1929–1958, 2014



\end{thebibliography}



\end{document}
